Article Title

### 2013-10-04 sections/Estimators.tex
minor

Just as in estimator A, $\hat\Sigma_0$ is shrunk toward $\hat T_d$ by linear mixing controlled by shrinkage intensity $\lambda\in[0,1]$.
\begin{equation}
\hat\Sigma_{d,\lambda}^\mathcal{B} = (1-\lambda)\hat\Sigma_0 + \lambda\hat T_d
\end{equation}
and the optimal values of $d$ and $\lambda$ are found by cross-validation within the training set.

@@

The covariance matrix estimate is then 
\begin{equation}
\hat\Sigma_\rho = \hat S^{-1}
\quad\mbox{with}\quad
\hat S = \argmin\limits_{\substack{S\succ 0 \\ \|S\|_0 = \rho}} \loss{S^{-1},\hat\Sigma_0}   
\end{equation}
where $S\succ 0$ signifies the constraint that $S$ be positive-definite. $\|S\|_0=\rho$ signifies the constraint  that matrix $S$ have $\rho$ non-zero coefficients.
Solving this approximation in this form is computationally challenging. The problem can be made computationally tractable by relaxing the $L_0$ norm to the $L_1$ norm, which converts the problem into one of convex optimization \cite{Donoho:2000}.  The resulting algorithm, known as \emph{graphical lasso} or \emph{GLASSO}  \cite{Meinshausen:2006,Yuan:2007,Banerjee:2008,Friedman:2008}, produces the following estimator  
\begin{equation}
\hat\Sigma_\lambda^\mathcal{C} = \hat S^{-1}
\quad\mbox{with}\quad
\hat S = \argmin\limits_{S\succ 0} \loss{S^{-1},\hat\Sigma_0} + \lambda \|S\|_1
\end{equation}
where $\lambda \|S\|_1$ is the $L_1$ norm of the matrix. \TODO{clarify}.

@@

\subsubsection*{Estimator $\mathcal D$: Sparse inverse + low-rank}
\emph{Estimator $\mathcal D$} produces a low-dimensional estimate by finding an apprxomation of $\hat\Sigma_0$ approximating the sample covariance matrix such that its inverse is the sum of a spase matrix and a low-rank matrix. Covariance matrices of this form correspond to Gaussian graphical models of the form depicted in Fig.~\ref{fig:02}D.

The inverse $S=\Sigma^{-1}$ of the covariance matrix of a GGM constitutes the graph of conditional dependencies (interactions) between the units.  With the assumption of sparse organization of interactions in the network, $S$ is assumed to be sparse.  When the observed units are part of a larger GGM that includes other latent units, let the negative inverse $S^*$ of the joint distribution of both observed and latent units be composed of four partitions
\begin{equation}
S^* = 
\begin{pmatrix}
S_{11} & S_{12} \\
S_{12}^\T & S_{22} 
\end{pmatrix}
\end{equation}
where partition $S_{11}$ describes the interactions between the visible units, $S_{12}$ describe the interactions between visible and latent units, and $S_{22}$ describes the interactions between the latent units. 
Then the covariance matrix of between the observed unit is 
\begin{equation}
\Sigma = \left(S_{11} - S_{12}S_{22}^{-1}S_{12}^\T\right)^{-1}
\end{equation} 
The rank of matrix $S_{12}S_{22}^{-1}S_{12}$ equals the number of latent units. Rather than solving for the precise dependency structure with and between latent units in matrices $S_{12}$ and $S_{22}$, we simply replace the matrix $ S_{12}S_{22}^{-1}S_{12}$ with on low-rank matrix $L_d= S_{12}S_{22}^{-1}S_{12}$ with rank $d$.

Then we obtain estimator $\hat\Sigma_{d,\rho}$, parameterized by the sparsity parameter $\rho$ and  the number of latent units $d$:
\begin{equation}
\hat\Sigma_{d,\rho} = \left(\hat L-\hat S\right)^{-1}
\quad\mbox{where}\quad
(\hat S, \hat L) = \argmin\limits_{\substack{S,L\\ (L-S)\succ 0 \\ \|S\|_0=\rho \\ L\succeq 0 \\ \rank(L) \le d}} \loss{(L-S)^{-1},\Sigma_0}
\end{equation}

Again, in this formulation, the problem is computationally intractible.  The problem can be made convex by replacing the $L_0$ norm with $L_1$ norm. The resulting algorith, known as \emph{latent-variable graphical lasso} or \emph{LV-GLASSO} \cite{Chandrasekaran:2010,Ma:2013}, produces estimator $\hat\Sigma_{d,\lambda}^{\mathcal D}$:
\begin{equation}
\hat\Sigma_{d,\lambda} ^{\mathcal D} = \left(\hat L-\hat S\right)^{-1}
\quad\mbox{where}\quad
(\hat S, \hat L) = \argmin\limits_{\substack{ S,L \\ (L-S)\succ 0 \\ L\succeq 0 \\ \rank(L) \le d}} \loss{(L-S)^{-1},\Sigma_0} + \lambda \| S \|_1 
\end{equation}
The optimal values of hyperparameters $\lambda$ and $d$ are found cross-validation within the training dataset.

>>>>

Just as in estimator $\mathcal A$, $\hat\Sigma_0$ is shrunk toward $\hat T_d$ by linear mixing controlled by shrinkage intensity $\lambda\in[0,1]$.
\begin{equation}
\hat\Sigma_{d,\lambda}^\mathcal{B} = (1-\lambda)\hat\Sigma_0 + \lambda\hat T_d
\end{equation}
and the optimal values of $d$ and $\lambda$ are found by cross-validation within the training set.

@@

The covariance matrix estimate is then 
\begin{equation}
\hat\Sigma_\rho = \hat S^{-1}
\quad\mbox{with}\quad
\hat S = \argmin\limits_{\substack{S\succ 0 \\ \|S\|_0 \le \rho}} \loss{S^{-1},\hat\Sigma_0}   
\end{equation}
where $S\succ 0$ signifies the constraint that $S$ be positive-definite. $\|S\|_0\le\rho$ signifies the constraint  that matrix $S$ have at most $\rho$ non-zero coefficients.
Solving this approximation in this form is computationally challenging. The problem can be made computationally tractable by relaxing \TODO{use "complex relaxation"} the $L_0$ norm to the $L_1$ norm, which converts the problem into one of convex optimization \cite{Donoho:2000}.  The resulting algorithm, known as \emph{graphical lasso} or \emph{GLASSO}  \cite{Meinshausen:2006,Yuan:2007,Banerjee:2008,Friedman:2008}, produces the following estimator  
\begin{equation}
\hat\Sigma_\lambda^\mathcal{C} = \hat S^{-1}
\quad\mbox{with}\quad
\hat S = \argmin\limits_{S\succ 0} \loss{S^{-1},\hat\Sigma_0} + \lambda \|S\|_1
\end{equation}
where $\lambda \|S\|_1$ is the $L_1$ norm of the matrix. \TODO{clarify}.

@@

\subsubsection*{Estimator $\mathcal D$: Sparse + low-rank inverse}
\emph{Estimator $\mathcal D$} produces a low-dimensional estimate by approximating $\hat\Sigma_0$ with a matrix whose inverse is the sum of a spase matrix and a low-rank matrix. Covariance matrices of this form correspond to Gaussian graphical models of the form depicted in Fig.~\ref{fig:02}D.

The inverse $S=\Sigma^{-1}$ of the covariance matrix of a GGM constitutes the graph of conditional dependencies (interactions) between the units.  With the assumption of sparse organization of interactions in the network, $S$ is assumed to be sparse.  When the observed units are part of a larger GGM that includes other latent units, let the negative inverse $S^*$ of the joint distribution of both observed and latent units be composed of four partitions
\begin{equation}
S^* = 
\begin{pmatrix}
S_{11} & S_{12} \\
S_{12}^\T & S_{22} 
\end{pmatrix}
\end{equation}
where partition $S_{11}$ describes the interactions between the visible units, $S_{12}$ describe the interactions between visible and latent units, and $S_{22}$ describes the interactions between the latent units. 
Then the covariance matrix of between the observed unit is 
\begin{equation}
\Sigma = \left(S_{11} - S_{12}S_{22}^{-1}S_{12}^\T\right)^{-1}
\end{equation} 
The rank of matrix $S_{12}S_{22}^{-1}S_{12}$ equals the number of latent units. Rather than solving for the precise dependency structure with and between latent units in matrices $S_{12}$ and $S_{22}$, we simply replace the matrix $ S_{12}S_{22}^{-1}S_{12}$ with one low-rank matrix $L= S_{12}S_{22}^{-1}S_{12}$.

Then we obtain estimator $\hat\Sigma_{d,\rho}$, parameterized by the sparsity parameter $\rho$ and  the number of latent units $d$:
\begin{equation}
\hat\Sigma_{d,\rho} = \left(\hat S-\hat L\right)^{-1}
\quad\mbox{where}\quad
(\hat S, \hat L) = \argmin\limits_{\substack{S,L\\ (S-L)\succ 0 \\ \|S\|_0\le\rho \\ L\succeq 0 \\ \rank(L) \le d}} \loss{(S-L)^{-1},\Sigma_0}
\end{equation}

Again, in this formulation, the approximation problem is computationally intractible.  The problem can be made convex by replacing the $L_0$ norm with $L_1$ norm. The resulting algorith, known as \emph{latent-variable graphical lasso} or \emph{LV-GLASSO} \cite{Chandrasekaran:2010,Ma:2013}, produces estimator $\hat\Sigma_{d,\lambda}^{\mathcal D}$:
\begin{equation}
\hat\Sigma_{d,\lambda} ^{\mathcal D} = \left(\hat S-\hat L\right)^{-1}
\quad\mbox{where}\quad
(\hat S, \hat L) = \argmin\limits_{\substack{ S,L \\ (S-L)\succ 0 \\ L\succeq 0 \\ \rank(L) \le d}} \loss{(S-L)^{-1},\Sigma_0} + \lambda \| S \|_1 
\end{equation}
The optimal values of hyperparameters $\lambda$ and $d$ are found cross-validation within the training dataset.
